Evaluate PEER in each cohort and brain region

### 2020-11-18 combined_analysis/eval_resid_in_each.Rmd
Initial commit

---
title: "Evaluate residuals in each cohort and brain region"
subtitle: ''
author: "Developed by [Gabriel Hoffman](http://gabrielhoffman.github.io/)"
date: "Run on `r Sys.time()`"
documentclass: article
output: 
  html_document:
  toc: true
  smart: false
---

@@

library(githubr)
parentId = 'syn22012942';
activityName = 'Evaluate residuals in each cohort and brain region';
activityDescription = 'Evaluate residuals in each cohort and brain region';

@@

```{r}
CODE <- Folder(name = "Evaluate residuals in each cohort and brain region", parentId = "syn22012942")
CODE <- synStore(CODE)

@@

  # get formula
  j = unlist(sapply(names(form.lst), function(x) grep(x, datID)))
  form_use = form.lst[[names(j)]]
  # apply voom
  vobj = voomWithDreamWeights(dge[1:200,], form_use, info, save.plot=TRUE, BPPARAM = SnowParam(18))

@@

  PEER_setNk(model,2)

>>>>

---
title: "Evaluate PEER in each cohort and brain region"
subtitle: ''
author: "Developed by [Gabriel Hoffman](http://gabrielhoffman.github.io/)"
date: "Run on `r Sys.time()`"
documentclass: article
output: 
  html_document:
  toc: true
  smart: false
---

@@

library(githubr)
parentId = 'syn22012942';
activityName = 'Evaluate PEER in each cohort and brain region';
activityDescription = 'Evaluate PEER in each cohort and brain region';

@@

```{r}
CODE <- Folder(name = "Evaluate PEER in each cohort and brain region", parentId = "syn22012942")
CODE <- synStore(CODE)

@@

  # get formula
  j = unlist(sapply(names(form.lst), function(x) grep(x, datID)))
  form_use = form.lst[[names(j)]]
  # apply voom
  vobj = voomWithDreamWeights(dge, form_use, info, save.plot=TRUE, BPPARAM = SnowParam(18))

@@

  PEER_setNk(model,20)
